Interlocks Mitigate Information Cascades in Large-Scale Social Learning

### 2024-10-29 manuscript.tex
Updates from Overleaf

\section{Introduction}
Large collaborations face a dilemma:
participatory governance is both
highly desirable and notorioulsy difficult
to implement in large groups.
Elinor Ostrom's empircal study of commons governance identified participatory rule-making
as one of the key principles necessary for the success and longevity of resource regimes
\cite{ostrom_collective_2000, ostrom_governing_1990}.
Participatory governance, particularly participatory deliberation,
enables the aggregation and synthesis of diverse knowledge
\cite{
dewey_creative_1940,
anderson_epistemology_2006,
ackerman_deliberation_2002},
benefits from the wisdom of crowds
\cite{
surowiecki_wisdom_2005,
hill_group_1982,
hong_groups_2004,
golub_naive_2010,
galton_vox_1907},
identifies and resolves conflicts
\cite{gentry_consensus_1982},
and incentivizes future cooperation by increasing perceptions of trust and fairnesss
\cite{
ostrom_collective_2000,
bowles_endogenous_1998}.
Unfortunately, as groups grow larger so does the difficulty of participatory governance.
The challenges of participatory governance in large groups include:
increased time and effort needed to reach decisions
\cite{
fishkin_voice_1997,
gentry_consensus_1982,
steiner_group_1972},
the emergence of power inequalities
\cite{
freeman_tyranny_1972,
shaw_laboratories_2014,
kittur_power_2007,
boehm_egalitarian_1993},
and counterproductive social dynamics such as
information cascades \cite{banerjee_simple_1992},
polarization \cite{schkade_what_2007},
social loafing \cite{karau_social_1993},
and the majority illusion \cite{lerman_majority_2015}.
Yet examples of successful large-scale participatory governance do exist, including Wikipedia \cite{giles_internet_2005, keegan_evolution_2017, forte_scaling_2008}, free and open source software projects \cite{benkler_coases_2002}, grassroots protest and crisis-response networks \cite{manilov_occupy_2013, tufekci_twitter_2017,
gonzalez-bailon_networked_2016,
landau_place-based_2017,
brugh_combining_2019}
and self-managed organizations
\cite{laloux_reinventing_2014,monsen_buurtzorg_2013,robertson_holacracy_2015}.
These examples often rely on the unprecedented fast, inexpensive, many-to-many communication afforded by the internet.
But not all intenet-enabled participatory collaborations succeed \cite{tufekci_twitter_2017, geiger_does_2009}. Why do some succeed while others fail?

In this paper, we begin with a review of the literature on large-scale participatory decision-making and related topics.
We focus in particular on empirical studies of successful large-scale participatory projects, looking for commonalities.
We then focus on one such commonality: social network structure,
specifically interlock networks.
We also narrow our focus to social learning:
the process by which individuals revise their beliefs and opinions
based on obersvations and interactions with others---a
core part of participatory decision-making.
Finally, we develop an agent-based model
to test the effects of interlock networks on social learning
in large groups.
Our findings suggest that interlock network structure may contribute to the success of large-scale participatory projects by providing protection from information cascades and polarization.

@@

Readers may understandably question how well a computer simulation can provide insight into the rich complexities of human behavior.
As with all models, computer and otherwise,
the usefulness of our methodology depends on the soundness of our simplifying assumptions and the applicability of our outcome measures.
So we base both on a thorough review of the observational literature.
If our model finds that the conditions present in real-world participatory groups lead to the outcomes observed in real-world participatory groups,
we can provide insight on how and why those conditions might lead to those outcomes.

@@

\subsection{Collaboration and Network Structure}
As we will elaborate below,
we find that real-world examples of successful large-scale participatory collaborations
often share a common trait:
interlocking social network structure.
Here, we use ``network'' in the sense of a set of entities with dyadic relationships between them \cite{newman_networks_2018}, e.g.,
individuals linked to other individuals through direct communication.
Similarly, we use ``structure'' to refer to the configuration of individual dyadic relationships and connnections rather than in the ``social system'' sense, e.g., the difference in communication links between a roundtable discussion and a lecture.
An {\em interlocking network} or {\em interlock}
is a network in which groups of entities are connected (interlocked)
through shared individual constituents \cite{taylor_world_2015}.
As a much-studied example,
an interlocking directorate is a network of corporations
in which two corporations (the groups) are considered connected if any individual director (the constituent) belongs to both of their boards 
\cite{mizruchi_what_1996}.
Or as a more modern example,
collaborative interactions on Wikipedia take place on individual articles, their per-article talk pages, and on topical WikiProject pages \cite{platt_network_2018}.
In this example, articles/talk pages/projects are the groups, and individual editors are the constituents.

The relationship between network structure and large-scale participatory collaboration may not be immediately obvious.
In large collaborations, while it may be the case than anyone {\em can} talk to anyone else, it is not the case that everyone {\em does} talk to everyone else.
The number of potential interactions is much greater than the capacity of the collaborators.
This fact implies a network structure: who interacts with whom.
While hierarchical ``tree'' newtorks are a practical way to interconnect a large group of people,
as in a military chain of command or corporate org chart,
they privilege some group members above others.
Participatory collaboration requires different structures.
In the context of self-organized collaboration, most network-based analyses have focused on 
small-world networks \cite{watts_collective_1998}
and preferential attachment networks \cite{barabasi_emergence_1999},
rather than interlocks,
with the notable exception of Salehi \& Bernstein's work on network rotation \cite{salehi_hive:_2018}.

There is considerable evidence that group composition
\cite{hill_group_1982,
nishi_inequality_2015,
robert_jr_differences_2018,
sydow_diversity_2017,
lerner_diverse_2018,
arazy_information_2011}
and social network structure
\cite{
kearns_experiments_2012,
barkoczi_social_2016,
salehi_hive:_2018,
mason_propagation_2008,
mason_collaborative_2012}
can influence the success of a collaboration.
Interlocking structure has implications for both of these factors.
By dividing an entire collaborative project into smaller groups,
interlocks influence group size and group composition,
potentially sidestepping some of the pitfalls of large group collaboration.
Similarly, by creating interconnections between groups through mutual membership,
interlocks influence the overall strucutral properties of the network.
In turn, those structural properties influence the speed and flow of information diffusion through the entire population of collaborators.

\subsection{Social Learning}
To begin to disentangle the multiple ways interlocking structure might influence the large participatory collaborations,
we focus on a subset of possible factors.
Specifically, we model collaborations as {\em social learning} processes \cite{barkoczi_social_2016, mason_collaborative_2012, hong_interpreted_2009, degroot_reaching_1974},
in which homogeneous agents exchange information and choose preferred solutions to a problem based on a combination of individual assessments of solution quality and information received from peers.
In this model, agents can apply different
{\em social learning strategies} to integrate socially acquired information with their own individual assesments.
Strategies can be classified as {\em conformist} when social influence is prioritized over individual assesments and {\em individualist} in the opposite case.
While this model leaves out many real-world collaboarative considerations,
ranging from the deep
(e.g.,
argumentation \cite{fishkin_voice_1997, mansbridge_minimalist_2015},
identity \cite{bail_breaking_2022,schkade_what_2007},
implicit bias \cite{amodio_stereotyping_2006},
interpersonal conflict\cite{whiting_did_2019})
to the mundane (e.g.,
mood, 
conversational tone),
solution-quality-based considerations are common across collaborations,
and are considered by many scholars to be a normative or even necessary
part of participatory decision-making
\cite{mansbridge_minimalist_2015}.
We thus propose this work as an starting point for understanding the seemingly-important role of interlocks in large-scale participatory collaboration, leaving additional considerations as crucial future work.

@@

\subsection{Contributions}
In this paper, we present the following contributions:
\begin{itemize}
\item{We show that social-learning on interlocks outperforms small-world and preferential attachment networks for some social learning strategies, and performs comparably for others (RQ 1).}
\item{Specifically, we show that in groups using a conformist social learning strategy, interlocks outperform other networks (RQ 3).
We attribute this improvement to a protective effect against information cascades that lead to the adoption of popular but sub-optimal solutions.}
\item{We also show that interlocks do not result in notably slower convergence, even in cases where they improve solution quality (RQ 2).}
\item{Finally, we show that interlocks reduce polarization when agents are using a conformist strategy (RQ 4).
Again, we attribute this result to a protective effect against information cascades.}
\end{itemize}
Taken together, our findings show that interlocks provide a protective effect against information cascades in large-scale social learning, which improves the performance of conformist strategies while resulting in similar performance for individualist strategies.
This protective effect may contribute to the relative success observed in large participatory collaborations with interlocking network structure.

@@

Examples of large participatory collaborations have become increasingly common in recent years,
and some have achieved surprising levels of success.
In particular, many of these recent successes rely on the fast, inexpensive, many-to-many communication afforded by the internet,
which has enabled an environment Jochai Benkler calls the ``networked information economy''
\cite{benkler_wealth_2006}.
Wikipedia, the popular online encyclopedia has been produced by millions of editors (47.6 million for just the English language edition at time of writing \cite{noauthor_list_2024, noauthor_wikipediawikipedians_2024})
using consensus-based, participatory decision-making \cite{keegan_evolution_2017, forte_scaling_2008}.
Despite common wisdom regarding the impossibility of large-scale participatory governance,
Wikipedia has been found comparable in quality to traditionally-edited encyclopedias \cite{giles_internet_2005},
leading to the popular Wikipedian in-joke that
``The problem with Wikipedia, is that it only works in practice. In theory, it's a total disaster'' \cite{elsharbaty_editing_2016}.
Similarly, Free and Open-Source Software (FOSS),
which is also highly participatory,
has achieved a level of success that rivals traditionally-produced software
\cite{benkler_wealth_2006, raymond_cathedral_1999}.
As one example, the FOSS operating system Linux is the most popular OS for internet servers and the core of the Android OS for mobile devices.
In a business context, examples of participatory worker self-management can be found in both corporate and cooperative contexts \cite{laloux_reinventing_2014, lee_self-managing_2017}.
Examples include Zappos.com's evolving use of the Holacracy system
\cite{robertson_holacracy_2015, groth_zappos_2020}
and the Buurtzorg model of homecare
\cite{monsen_buurtzorg_2013, gray_home_2015}.
Grassroots social movements and crisis-response groups have also made use of participatory governance.
The Occupy movment embraced participatory governance \cite{detar_intertwinkles:_2013, gonzalez-bailon_networked_2016}
which resurfaced in the 60,000 self-organized volunteers of the Occupy Sandy crisis-response efforts \cite{landau_place-based_2017, brugh_combining_2019}.
Similarly, participatory practices were a key part of the 2013 Gezi Park protests
\cite{tufekci_twitter_2017}.

\subsection{Interlocks}
When reviewing these examples, a remarkably common pattern stands out: interlocking network strucutre.
In these successful examples of large-scale participatory projects,
communication is frequently organized into small participatory groups of peers, based on interest, region, function, or simply happenstance.
These groups are then interconnected through individuals who participate in multiple groups.
We reproduce excerpts from several examples here to demonstrate the ubiquity of this pattern.

Occupy Wall Street and Occupy Sandy \cite{manilov_occupy_2013}:
\begin{quote}
One of the greatest strengths of the Occupy movement has been its willingness to decentralize decision making into networks built on a foundation of small groups that move easily between online and real-world activities.
\end{quote}

@@

\subsection{Social Learning Strategies}

\subsection{Network Types}

TODO

\section{Methods\label{sec:methods}}
Agent-based model

>>>>

\section{Introduction}
Large collaborations face a dilemma:
participatory governance is both
highly desirable and notoriously difficult
to implement in large groups.
Elinor Ostrom's empirical study of commons governance identified participatory rule-making
as one of the key principles necessary for the success and longevity of resource regimes
\cite{ostrom_collective_2000, ostrom_governing_1990}.
Participatory governance, particularly participatory deliberation,
enables the aggregation and synthesis of diverse knowledge
\cite{
dewey_creative_1940,
anderson_epistemology_2006,
ackerman_deliberation_2002},
benefits from the wisdom of crowds
\cite{
surowiecki_wisdom_2005,
hill_group_1982,
hong_groups_2004,
golub_naive_2010,
galton_vox_1907},
identifies and resolves conflicts
\cite{gentry_consensus_1982},
and incentivizes future cooperation by increasing perceptions of trust and fairness
\cite{
ostrom_collective_2000,
bowles_endogenous_1998}.
Unfortunately, as groups grow larger so does the difficulty of participatory governance.
The challenges of participatory governance in large groups include:
increased time and effort needed to reach decisions
\cite{
fishkin_voice_1997,
gentry_consensus_1982,
steiner_group_1972},
the emergence of power inequalities
\cite{
freeman_tyranny_1972,
shaw_laboratories_2014,
kittur_power_2007,
boehm_egalitarian_1993},
and counterproductive social dynamics such as
information cascades \cite{banerjee_simple_1992},
polarization \cite{schkade_what_2007},
social loafing \cite{karau_social_1993},
and the majority illusion \cite{lerman_majority_2015}.
Yet examples of successful large-scale participatory governance do exist, including Wikipedia \cite{giles_internet_2005, keegan_evolution_2017, forte_scaling_2008}, free and open source software projects \cite{benkler_coases_2002}, grassroots protest and crisis-response networks \cite{manilov_occupy_2013, tufekci_twitter_2017,
gonzalez-bailon_networked_2016,
landau_place-based_2017,
brugh_combining_2019}
and self-managed organizations
\cite{laloux_reinventing_2014,monsen_buurtzorg_2013,robertson_holacracy_2015}.
These examples often rely on the unprecedented fast, inexpensive, many-to-many communication afforded by the internet.
But not all internet-enabled participatory collaborations succeed \cite{tufekci_twitter_2017, geiger_does_2009}. Why do some succeed while others fail?

In this paper, we begin with a review of the literature on large-scale participatory decision-making and related topics.
We focus, in particular, on empirical studies of successful large-scale participatory projects, looking for commonalities.
We then focus on one such commonality: social network structure,
specifically interlock networks.
We also narrow our focus to social learning:
the process by which individuals revise their beliefs and opinions
based on observations and interactions with others---a core part of participatory decision-making.
Finally, we develop an agent-based model
to test the effects of interlock networks on social learning
in large groups.
Our findings suggest that interlock network structure may contribute to the success of large-scale participatory projects by providing protection from information cascades and polarization.

@@

Readers may understandably question how well a computer simulation can provide insight into the rich complexities of human behavior.
As with all models, computer and otherwise,
the usefulness of our methodology depends on the soundness of our simplifying assumptions and the applicability of our outcome measures.
So we base both on a thorough review of the observational literature.
If our model finds that the conditions present in real-world participatory groups lead to the outcomes observed in real-world participatory groups,
we can provide insight into how and why those conditions might lead to those outcomes.

@@

\subsection{Collaboration and Network Structure}
As we will elaborate below,
we find that real-world examples of successful large-scale participatory collaborations
often share a common trait:
interlocking social network structure.
Here, we use ``network'' in the sense of a set of entities with dyadic relationships between them \cite{newman_networks_2018}, e.g.,
individuals linked to other individuals through direct communication.
Similarly, we use ``structure'' to refer to the configuration of individual dyadic relationships and connections rather than in the ``social system'' sense, e.g., the difference in communication links between a roundtable discussion and a lecture.
An {\em interlocking network} or {\em interlock}
is a network in which groups of entities are connected (interlocked)
through shared individual constituents \cite{taylor_world_2015}.
As a much-studied example,
an interlocking directorate is a network of corporations
in which two corporations (the groups) are considered connected if any individual director (the constituent) belongs to both of their boards 
\cite{mizruchi_what_1996}.
Or as a more modern example,
collaborative interactions on Wikipedia take place on individual articles, their per-article talk pages, and on topical WikiProject pages \cite{platt_network_2018}.
In this example, articles/talk pages/projects are the groups, and individual editors are the constituents.

The relationship between network structure and large-scale participatory collaboration may not be immediately obvious.
In large collaborations, while it may be the case that anyone {\em can} talk to anyone else, it is not the case that everyone {\em does} talk to everyone else.
The number of potential interactions is much greater than the capacity of the collaborators.
This fact implies a network structure: who interacts with whom.
While hierarchical ``tree'' networks are a practical way to interconnect a large group of people,
as in a military chain of command or corporate org chart,
they privilege some group members above others.
Participatory collaboration requires different structures.
In the context of self-organized collaboration, most network-based analyses have focused on 
small-world networks \cite{watts_collective_1998}
and preferential attachment networks \cite{barabasi_emergence_1999},
rather than interlocks,
with the notable exception of Salehi \& Bernstein's work on network rotation \cite{salehi_hive:_2018}.

There is considerable evidence that group composition
\cite{hill_group_1982,
nishi_inequality_2015,
robert_jr_differences_2018,
sydow_diversity_2017,
lerner_diverse_2018,
arazy_information_2011}
and social network structure
\cite{
kearns_experiments_2012,
barkoczi_social_2016,
salehi_hive:_2018,
mason_propagation_2008,
mason_collaborative_2012}
can influence the success of a collaboration.
Interlocking structure has implications for both of these factors.
By dividing an entire collaborative project into smaller groups,
interlocks influence group size and group composition,
potentially sidestepping some of the pitfalls of large group collaboration.
Similarly, by creating interconnections between groups through mutual membership,
interlocks influence the overall structural properties of the network.
In turn, those structural properties influence the speed and flow of information diffusion through the entire population of collaborators.

\subsection{Social Learning}
To begin to disentangle the multiple ways interlocking structure might influence the large participatory collaborations,
we focus on a subset of possible factors.
Specifically, we model collaborations as {\em social learning} processes \cite{barkoczi_social_2016, mason_collaborative_2012, hong_interpreted_2009, degroot_reaching_1974},
in which homogeneous agents exchange information and choose preferred solutions to a problem based on a combination of individual assessments of solution quality and information received from peers.
In this model, agents can apply different
{\em social learning strategies} to integrate socially acquired information with their own individual assessments.
Strategies can be classified as {\em high-connformity} when social influence is prioritized over individual assessments and {\em low-conformity} in the opposite case.
While this model leaves out many real-world collaborative considerations,
ranging from the deep
(e.g.,
argumentation \cite{fishkin_voice_1997, mansbridge_minimalist_2015},
identity \cite{bail_breaking_2022,schkade_what_2007},
implicit bias \cite{amodio_stereotyping_2006},
interpersonal conflict\cite{whiting_did_2019})
to the mundane (e.g.,
mood, 
conversational tone),
solution-quality-based considerations are common across collaborations,
and are considered by many scholars to be a normative or even necessary
part of participatory decision-making
\cite{mansbridge_minimalist_2015}.
We thus propose this work as an starting point for understanding the seemingly-important role of interlocks in large-scale participatory collaboration, leaving additional considerations as crucial future work.

@@

\subsection{Contributions}
In this paper, we present the following contributions:
\begin{itemize}
\item{We show that social-learning on interlocks outperforms small-world and preferential attachment networks for some social learning strategies, and performs comparably for others (RQ 1).}
\item{Specifically, we show that in groups using a conformist social learning strategy, interlocks outperform other networks (RQ 3).
We attribute this improvement to a protective effect against information cascades that lead to the adoption of popular but sub-optimal solutions.}
\item{We also show that interlocks do not result in notably slower convergence, even in cases where they improve solution quality (RQ 2).}
\item{Finally, we show that interlocks reduce polarization when agents are using a conformist strategy (RQ 4).
Again, we attribute this result to a protective effect against information cascades.}
\end{itemize}
Taken together, our findings show that interlocks provide a protective effect against information cascades in large-scale social learning, which improves the performance of high-conformity strategies while resulting in similar performance for low-conformity strategies.
This protective effect may contribute to the relative success observed in large participatory collaborations with interlocking network structure.

@@

Examples of large participatory collaborations have become increasingly common in recent years,
and some have achieved surprising levels of success.
In particular, many of these recent successes rely on the fast, inexpensive, many-to-many communication afforded by the internet,
which has enabled an environment Jochai Benkler calls the ``networked information economy''
\cite{benkler_wealth_2006}.
Wikipedia, the popular online encyclopedia has been produced by millions of editors (47.6 million for just the English language edition at time of writing \cite{noauthor_list_2024, noauthor_wikipediawikipedians_2024})
using consensus-based, participatory decision-making \cite{keegan_evolution_2017, forte_scaling_2008}.
Despite common wisdom regarding the impossibility of large-scale participatory governance,
Wikipedia has been found comparable in quality to traditionally-edited encyclopedias \cite{giles_internet_2005},
leading to the popular Wikipedian in-joke that
``The problem with Wikipedia, is that it only works in practice. In theory, it's a total disaster'' \cite{elsharbaty_editing_2016}.
Similarly, Free and Open-Source Software (FOSS),
which is also highly participatory,
has achieved a level of success that rivals traditionally-produced software
\cite{benkler_wealth_2006, raymond_cathedral_1999}.
As one example, the FOSS operating system Linux is the most popular OS for internet servers and the core of the Android OS for mobile devices.
In a business context, examples of participatory worker self-management can be found in both corporate and cooperative contexts \cite{laloux_reinventing_2014, lee_self-managing_2017}.
Examples include Zappos.com's evolving use of the Holacracy system
\cite{robertson_holacracy_2015, groth_zappos_2020}
and the Buurtzorg model of homecare
\cite{monsen_buurtzorg_2013, gray_home_2015}.
Grassroots social movements and crisis-response groups have also made use of participatory governance.
The Occupy movement embraced participatory governance \cite{detar_intertwinkles:_2013, gonzalez-bailon_networked_2016}
which resurfaced in the 60,000 self-organized volunteers of the Occupy Sandy crisis-response efforts \cite{landau_place-based_2017, brugh_combining_2019}.
Similarly, participatory practices were a key part of the 2013 Gezi Park protests
\cite{tufekci_twitter_2017}.

\subsection{Interlocks}
When reviewing these examples, a remarkably common pattern stands out: interlocking network structure.
In these successful examples of large-scale participatory projects,
communication is frequently organized into small participatory groups of peers based on interest, region, function, or simply happenstance.
These groups are then interconnected through individuals who participate in multiple groups.
We reproduce excerpts from several examples here to demonstrate the ubiquity of this pattern.

Occupy Wall Street and Occupy Sandy \cite{manilov_occupy_2013}:
\begin{quote}
One of the greatest strengths of the Occupy movement has been its willingness to decentralize decision-making into networks built on a foundation of small groups that move easily between online and real-world activities.
\end{quote}

@@

\subsection{Social Learning Strategies}
The behavior of agents is defined by a {\em social learning strategy}.
These strategies are sets of rules that instruct an agent how to interact
with its neighbors and how to update its beliefs based on that interaction.
Different social learning strategies model different real-world behaviors.
They also make different assumptions about the capabilities of agents to
evaluate their own beliefs and the beliefs of their neighbors.
In this paper we follow the strategies defined by Barkoczi and Galesic \cite{barkoczi_social_2016}.

\subsubsection{Best-Neighbor}
The {\em best-neighbor} strategy is a naive, greedy strategy.
Agents simply evaluate the quality of each neighbor's candidate solution,
and adopt the best one.
In general, greedy algorithms are fast and efficient, but often converge
to sub-optimal local maxima.
Note that this strategy also assumes agents are capable of objectively
evaluating which of two solutions is better.
In other words, given two candidate solutions $s$ and $s^\prime$,
they can evaluate whether $Q(s^\prime) > Q(s)$.
Note that this does not require that agents are capable of evaluating
the exact value of $Q(s)$.
Because this strategy prioritizes solution quality over solution popularity,
we calssify it as a {\em low-conformity} strategy.

\subsubsection{Conform}
The {\em conform} strategy is, as its name suggests,
a {\em high-conformity} strategy.
In this strategy, agents survey the solutions of their neighbors and
select the most popular strategy.
Ties are broken randomly.
In the case that no candidate solution has been adopted by more than one
neighbor,
the agent simply keeps its previous candidate.
We also assume the {\em critical learning} convention
\cite{barkoczi_social_2016, rendell_rogersparadox_2010},
in which agents will only adopt a popular candidate solution if it is better
than their own.
This strategy requires that given a candidate solution,
agents are able to determine whether it is objectively better than their own.
However, it does not require the capability to compare the quality of two
{\em arbitrary} candidates.
The conform strategy models real-world settings in which individuals are
unable or uninclined to compare the quality of all options before them,
but can determine whether a single popular option is an imporovement over one
they have experience with.

\subsubsection{Individual}
In addition to social learning, agents may also engage in {\em individual}
learning.
Following \cite{barkoczi_social_2016},
we model individual learning as a hill-climbing algorithm.
Agents try changing a single bit of their candidate solution and determine
whether the new candidate is an improvement.
These strategies represent exploration of incremental improvements on existing
solutions.
Repeatedly applying individual learning will eventually lead to a local
maximum.

\subsection{Network Types}
Once agents have a problem to solve, and a strategy for interacting with
their neighbors, they need to know who their neighbors are.
This section describes the social network topologies used in our model.

\subsubsection{Small-World}
In {\em small-world} networks
\cite{watts_collective_1998},
individuals are mostly linked to others in the
same spatial or geographic location,
but have some long-distance {\em shortcuts}.
The local ties create high {\em clustering}:
an individuals neighbors are likely to be neighbors to each other.
The shortcuts act as weak ties \cite{granovetter_strength_1973},
reducing the ``size'' (mean shortest path length)
of the network by creating short paths
between any two individuals.
In Watts-Strogatz small-world network \cite{watts_collective_1998},
individuals are assigned to locations on a ring and connected to their
$k$ nearest neighbors (not to be confused with $K$ from the NK model).
For each of an individuals links,
with a probability $\beta$,
the other end of the link is assigned to a random individual,
creating the shortcut edges.

\subsubsection{Preferential-Attachment}

\subsubsection{Interlocks}

\section{Methods\label{sec:methods}}

Agent-based model parameters

Random-Pod
